---
title: "The Impact of COVID-19 on Car Industry"
author: "Jiayue He, Haochen Liu, Xuefei Wang"
date: "December 3, 2021"
output:
  pdf_document:
    toc: yes
    toc_depth: '2'
---

```{r Front Matter, include=FALSE}

# clean up & set default chunk options
rm(list = ls())
knitr::opts_chunk$set(echo = FALSE)

# load packages
library(readxl)
library(ggplot2)
library(tidyverse)
library(dplyr)
library(mosaic)
library(lubridate)
library(data.table)
library(plotly)
library(dygraphs)
library(corrplot)
library(kableExtra)
library(car)
library(regclass)

# inputs
environment <- read.csv("environment.csv")
sale <- read.csv("TOTALSA.csv")
brandsale <- read_excel("TotalSalebyBrand.xlsx")
Sale2015 <- read_excel("Sale2015.xlsx")
Sale2016 <- read_excel("Sale2016.xlsx")
Sale2017 <- read_excel("Sale2017.xlsx")
```

\pagebreak
# Project Description

For this Capstone project, we choose to focus on Economics. Our leader, Jiayue He majors in applied statistics and minored in economics. Therefore, in the 
beginning, we would like to study the affection of producing masks on our environmental economics. However, after doing some research, we found it hard for us to combine the impact of producing masks on both the environment and the economy together. Then, we decided to move to some more common topics that also involved environmental economics. Our new issue is based on car performance before and after COVID to do some further research. Due to this being an observational study, we couldn't draw a cause-effect conclusion in this report.

Our datasets are from two websites, one is provided by the U.S. Environment Protection Agency (EPA), and another is from the Automotive industry Portal, MarkLines.

## Research Questions

**Research Question 1: How does the performance of the automobile industry affect our environment before and after COVID-19?**

**Research Question 2: How does car sales affect the environment? **

## Statistical Questions

**Statistical Question 1: Is there a relationship between the concentration of carbon dioxide and car weights, footprint, horsepower, fuel delivery, engine displacement?**

**Statistical Question 2: Is there a relationship between car sales and the concentration of carbon dioxide? **

## Variables

```{r variable}
variables <- read_excel("variables.xlsx")
kable(variables,booktabs = T) %>%
  kable_styling(latex_options = "HOLD_position", font_size = 7)
```

To demonstrate the impact of COVID-19, we create one column named *Covid* to indicate whether the model year is during COVID-19.
*Production* is created by adding  sale units for each branch per month.

# Exploratory Data Analysis (EDA)

Before employ the models, we have filter the condition and check for missing values. There are few missing values for specific model, Tesla. We replace the missing values with proper amounts based on the information from official websites.

```{r Data Cleaning, include=FALSE}

# The first resource cleaning
## selections 
year <- c('2015','2016','2017','2018','2019','2020')
environment1 <- filter(environment, Model.Year %in% year)

model <- c('All')

#environment1 <- filter(environment1, Manufacturer != model)
environment1 <- filter(environment1, ï..Manufacturer != model)


## rename variables to become more appropriate
names(environment1)[names(environment1) == 
                      'Model.Year'] <- 'Year'
names(environment1)[names(environment1) == 
                      'ï..Manufacturer'] <- 'Manufacturer'
names(environment1)[names(environment1) == 
                      'Real.World.CO2..g.mi.'] <- 'Real.World.CO2'
names(environment1)[names(environment1) == 
                      'Real.World.CO2_City..g.mi.'] <- 'Real.World.CO2_City'
names(environment1)[names(environment1) == 
                      'Real.World.CO2_Hwy..g.mi.'] <- 'Real.World.CO2_Hwy'
names(environment1)[names(environment1) == 
                      'Weight..lbs.'] <- 'Weight'
names(environment1)[names(environment1) == 
                      'Horsepower..HP.'] <- 'Horsepower'
names(environment1)[names(environment1) == 
                      'Footprint..sq..ft..'] <- 'Footprint'
names(environment1)[names(environment1) == 
                      'Fuel.Delivery...Gasoline.Direct.Injection..GDI.'] <- 
  'Fuel.Delivery.GDI'
 
## select variables that can be used 
environment1 <- 
  environment1 %>%
  select(Manufacturer, Year, X2.Cycle.MPG, Real.World.MPG, Real.World.MPG_City,
         Real.World.MPG_Hwy, Real.World.CO2, Real.World.CO2_City, Real.World.CO2_Hwy,
         Weight, Footprint, Horsepower, Fuel.Delivery.GDI, Engine.Displacement)

## change form of variables 
environment1$Year <- as.factor(environment1$Year)
environment1$X2.Cycle.MPG <- as.numeric(environment1$X2.Cycle.MPG)
environment1$Real.World.MPG <- as.numeric(environment1$Real.World.MPG)
environment1$Real.World.MPG_City <- as.numeric(environment1$Real.World.MPG_City)
environment1$Real.World.MPG_Hwy <- as.numeric(environment1$Real.World.MPG_Hwy)
environment1$Real.World.CO2 <- as.numeric(environment1$Real.World.CO2)
environment1$Real.World.CO2_City <- as.numeric(environment1$Real.World.CO2_City)
environment1$Real.World.CO2_Hwy <- as.numeric(environment1$Real.World.CO2_Hwy)
environment1$Weight <- as.numeric(environment1$Weight)
environment1$Footprint <- as.numeric(environment1$Footprint)
environment1$Horsepower <- as.numeric(environment1$Horsepower)
environment1$Fuel.Delivery.GDI <- as.numeric(environment1$Fuel.Delivery.GDI)

environment1$Engine.Displacement[environment1$Manufacturer == "Tesla"] <- 0
environment1$Engine.Displacement <- as.numeric(environment1$Engine.Displacement)

## Tesla carbon emission 

environment1$Real.World.CO2[environment1$Manufacturer == "Tesla" &
                              environment1$Year == "2015"] <- 400
environment1$Real.World.CO2[environment1$Manufacturer == "Tesla" &
                              environment1$Year == "2016"] <- 400
environment1$Real.World.CO2[environment1$Manufacturer == "Tesla" &
                              environment1$Year == "2017"] <- 400
environment1$Real.World.CO2[environment1$Manufacturer == "Tesla" &
                              environment1$Year == "2018"] <- 400
environment1$Real.World.CO2[environment1$Manufacturer == "Tesla" &
                              environment1$Year == "2019"] <- 420
environment1$Real.World.CO2[environment1$Manufacturer == "Tesla" & 
                              environment1$Year == "2020"] <- 400

# The second resource
## combine datasets
brandsale <- brandsale %>% filter(Brand != "Others")
brandsale_add <- merge(Sale2015, Sale2016, by = c("Brand","Month"))
brandsale_add <- merge(brandsale_add, Sale2017, by = c("Brand","Month"))
brandsale <- merge(brandsale_add, brandsale, by = c("Brand","Month"))

## change name
names(brandsale)[3] <- "Sale2015"
names(brandsale)[4] <- "Sale2016"
names(brandsale)[5] <- "Sale2017"
names(brandsale)[8] <- "Sale2018"
names(brandsale)[7] <- "Sale2019"
names(brandsale)[6] <- "Sale2020"

## calculate the total for each year
brandsale1 <-
  brandsale %>%
  select(Sale2015, Month) %>%
  group_by(Month)%>%
  summarise(total = sum(Sale2015))

brandsale2 <-
  brandsale %>%
  select(Sale2016, Month) %>%
  group_by(Month)%>%
  summarise(total = sum(Sale2016))

brandsale3 <-
  brandsale %>%
  select(Sale2017, Month) %>%
  group_by(Month)%>%
  summarise(total = sum(Sale2017))

brandsale4 <-
  brandsale %>%
  select(Sale2018, Month) %>%
  group_by(Month)%>%
  summarise(total = sum(Sale2018))

brandsale5 <-
  brandsale %>%
  select(Sale2019, Month) %>%
  group_by(Month)%>%
  summarise(total = sum(Sale2019))

brandsale6 <-
  brandsale %>%
  select(Sale2020, Month) %>%
  group_by(Month)%>%
  summarise(total = sum(Sale2020))


brandsale1 <- 
  brandsale1 %>%
  mutate(Month = seq(as.Date("2015-01-01",  format = "%Y-%m-%d"), 
                     length.out = 12, by = "month"))

brandsale2 <- 
  brandsale2 %>%
  mutate(Month = seq(as.Date("2016-01-01",  format = "%Y-%m-%d"),
                     length.out = 12, by = "month"))

brandsale3 <- 
  brandsale3 %>%
  mutate(Month = seq(as.Date("2017-01-01",  format = "%Y-%m-%d"),
                     length.out = 12, by = "month"))

brandsale4 <- 
  brandsale4 %>%
  mutate(Month = seq(as.Date("2018-01-01",  format = "%Y-%m-%d"), 
                     length.out = 12, by = "month"))

brandsale5 <- 
  brandsale5 %>%
  mutate(Month = seq(as.Date("2019-01-01",  format = "%Y-%m-%d"),
                     length.out = 12, by = "month"))

brandsale6 <- 
  brandsale6 %>%
  mutate(Month = seq(as.Date("2020-01-01",  format = "%Y-%m-%d"),
                     length.out = 12, by = "month"))

## combine three data
brandfinal <- bind_rows(brandsale1,brandsale2,brandsale3,
                        brandsale4,brandsale5,brandsale6)

## ascending the date
brandfinal <-
  brandfinal %>%
  arrange(Month)

# clean data for the first model
names(environment)[names(environment) == 'ï..Manufacturer'] <- 'Manufacturer'
research.data <- environment
research.data$Country <- "all"
research.data$Country[research.data$Manufacturer %in% c("Toyota","Mazda",
                                                        "Honda","Subaru",
                                                        "Nissan")] <- "Japan"
research.data$Country[research.data$Manufacturer %in% c("BMW","Mercedes",
                                                        "VW")] <- "German"
research.data$Country[research.data$Manufacturer %in% c("GM","Ford","Tesla",
                                                        "FCA")] <- "America"
research.data$Country[research.data$Manufacturer %in% c("Hyundai",
                                                        "Kia")] <- "Korea"

research.data <-
  research.data %>%
  filter(Country != "all")

colnames(research.data)[4] <- "Year"
colnames(research.data)[9] <- "Real.World.CO2"
colnames(research.data)[12] <- "Weight"
colnames(research.data)[13] <- "Footprint"
colnames(research.data)[15] <- "Horsepower"
colnames(research.data)[29] <- "Fuel.Delivery.GDI"

research.data <- research.data[c("Real.World.CO2","Country" ,"Year" ,"Weight" ,
                                 "Footprint" ,"Horsepower" ,"Fuel.Delivery.GDI",
                                 "Engine.Displacement")]

research.data <- research.data %>% drop_na()

clean_data <- research.data[!(research.data$Real.World.CO2=="-" |
                                research.data$Country =="-" | 
                                research.data$Year =="-" | 
                                research.data$Weight=="-" |
                                research.data$Footprint=="-" |
                                research.data$Horsepower=="-" | 
                                research.data$Footprint=="-" | 
                                research.data$Engine.Displacement=="-"),] 

clean_data <- transform(clean_data, Real.World.CO2 = as.numeric(Real.World.CO2),
                        Year = as.numeric(Year), Weight = as.numeric(Weight),
                        Footprint = as.numeric(Footprint),
                        Horsepower = as.numeric(Horsepower),
                        Fuel.Delivery.GDI = as.numeric(Fuel.Delivery.GDI), 
                        Engine.Displacement = as.numeric(Engine.Displacement))

clean_data$Covid <- as.integer(clean_data$Year == 2020)

# prepare data for  the second model
names(brandsale)[names(brandsale) == 'Brand'] <- 'Manufacturer'

brandsale_test <-
  brandsale %>%
  select(Manufacturer, Sale2020, Sale2019, Sale2018,Sale2017,Sale2016,Sale2015)

names(brandsale_test)[names(brandsale_test) == 'Sale2020'] <- 'Year2020'
names(brandsale_test)[names(brandsale_test) == 'Sale2019'] <- 'Year2019'
names(brandsale_test)[names(brandsale_test) == 'Sale2018'] <- 'Year2018'
names(brandsale_test)[names(brandsale_test) == 'Sale2017'] <- 'Year2017'
names(brandsale_test)[names(brandsale_test) == 'Sale2016'] <- 'Year2016'
names(brandsale_test)[names(brandsale_test) == 'Sale2015'] <- 'Year2015'

brandsale_test <-
  brandsale_test %>%
  gather(key = "Year", value = "production", 2:7)

brandsale_test$Year[brandsale_test$Year == "Year2020"] <- '2020'
brandsale_test$Year[brandsale_test$Year == "Year2019"] <- '2019'
brandsale_test$Year[brandsale_test$Year == "Year2018"] <- '2018'
brandsale_test$Year[brandsale_test$Year == "Year2017"] <- '2017'
brandsale_test$Year[brandsale_test$Year == "Year2016"] <- '2016'
brandsale_test$Year[brandsale_test$Year == "Year2015"] <- '2015'

brandsale_test$Year <- as.factor(brandsale_test$Year)

brandsale_test1 <-
  brandsale_test %>%
  group_by(Manufacturer, Year) %>%
  summarise(production = sum(production))

environment2 <-
  environment1 %>%
  group_by(Year,Manufacturer) %>%
  arrange(Year)

result <- left_join(environment1, brandsale_test1, by = c('Manufacturer', 'Year'))

result$Country <- "all"
result$Country[result$Manufacturer %in% c("Toyota","Mazda",
                                          "Honda","Subaru","Nissan")] <- "Japan"
result$Country[result$Manufacturer %in% c("BMW","Mercedes","VW")] <- "German"
result$Country[result$Manufacturer %in% c("GM","Ford","Tesla","FCA")] <- "America"
result$Country[result$Manufacturer %in% c("Hyundai","Kia")] <- "Korea"

result$Year <- as.integer(result$Year)
result$year2015 <- result$Year - 1

result$production <- result$production / 100000
```

## First plot
```{r barplot, fig.cap= "Car Sale Line Graph", fig.width=6, fig.height=4}
brandfinal1 <-
 brandfinal %>%
 select(total)
brandfinal2 <- ts(brandfinal1, frequency = 12, start = 2015)

plot.ts(brandfinal2)
```

From Figure 1, we can find how COVID-19 affected vehicle sales. From 2015 to 2019, we can see that there is not much difference of sales in each month. Without COVID-19, the year of 2020 has a similar sale trend. In fact, however, sales in 2020 illustrated å sharp change in some months, especially from March to June, which was the worst period caused by COVID-19. After June, the sales of 2020 started to recover and have been par on with data of previous year.

## Second plot
```{r correlation, fig.cap= "Correlation Plot", fig.width=4, fig.height=4}
# check Collinearity
model_corr_matrix <- cor(clean_data %>% 
                            select(Weight, Footprint, Horsepower, 
                                   Fuel.Delivery.GDI, Engine.Displacement),
                          use = "pairwise.complete.obs")

corrplot::corrplot(model_corr_matrix)
```

Based on Figure 2, Collinearity happens when two or more explanatory variables are correlated with each other. An extreme situation called multicollinearity, where collinearity exists between three or more variables even if no pair of variables has a particularly high correlation. This means that there is redundancy between explanatory variables. We can see from this figure that four variables *Weight*, *Footprint*, *Horsepower*, *Engine Displacement* show high relativity. Therefore, we decide to remove three of them and perserve *Weight* as one independent variable. Then we can retrain the linear regression model using *Country*, *Covid*, *Weight* and *Fuel Delivery GDI* as final explanatory variables.


# Statistical Analysis 
## Research Question 1
To check how the performance of the automobile industry affected our environment before and after COVID-19, we filtered out the related data including features like CO2, year, Footprint and others. We can omit the rows with missing values in some features, and thus obtain a clean dataset. 

After data preprocessing, we fit a linear regression model using the mentioned variables and set the *Real.World.CO2* emission as the response variable. At first, we select *Country*, *Covid*, *Weight*, *Footprint*, *Horsepower*, *Fuel.Delivery.GDI*, *Engine.Displacement* as explanatory variables. Then we check the regression assumptions like linearity of the data, normality of residuals, homogeneity of residuals variance and independence of residuals error terms. They appear in the Appendix.

```{r model1, include=FALSE}
# linear regression with Covid 
fit.lm1 <- lm(Real.World.CO2 ~ Country + Covid + Weight + Fuel.Delivery.GDI, 
              data = clean_data)
summary(fit.lm1)
```

| Variables         | Coefficients  | P-values | Is it significant|
| ----------------- |:-------------:| --------:|:----------------:|
| (Intercept)       |232.088776     | 1.34e-08 | Yes              |
| CountryGerman     | -1.361022     | 0.79468  | No               |
| CountryJapan      |-45.535800     | 2.69e-09 | Yes              |
| CountryKorea      |-28.035236     | 0.00394  | Yes              |
| Covid             |-10.655126     | 0.07479  | No               |
| Weight            |  0.045942     | 4.81e-07 | Yes              |
| Fuel.Delivery.GDI |-60.190618     |  < 2e-16 | Yes              |

From the linear regression result, we can find that the p-value of variable "Covid", greater than 0.05, is not relatively significant value and means that "Covid" has no affect on the environment. Hence we can draw our conclusion: the performance of the automobile industry will not affect our environment before and after COVID-19. 

In this regression model, the response variable is Real.World.CO2 (Estimated real-world CO2 measured by "5-cycle" tests). The explanatory variables are country (Cars made by which country), Coivd (Whether the year is 2020 or not ), Weight, and Fuel.Delivery.GDI (A fuel delivery system in gasoline internal combustion engines ). We also checked the assumptions required to use the Multiple Linear Regression Model (Please see the Appendix page). 

An example of interpretation for variable CountryJapan would be: keep other predictors unchanged, the mean CO2 of the output for the cars would improve their by 45.535800 g/mi compared to those cars made by American. Another example of interpretation for variable Fuel.Delivery.GDI would be: keep other predictors unchanged, each additional gdi rate would decrease their CO2 by 60.190618 g/mi. Compared with American cars, cars in Japan, Germany and  Korea will reduce carbon dioxide emissions.

Variables with significant p-values indicate that they would impact the environment in the different ways. In other words, Compared to American cars, cars in Japan and Korea have less air pollution. At that time, when the weight of the vehicle was heavier, the air pollution would be more serious.

## Research Question 2

```{r model2, include=FALSE}
fit.lm2 <- lm(Real.World.MPG ~ Country + year2015 + production + Weight 
              + Footprint + Horsepower + Fuel.Delivery.GDI + Engine.Displacement,
              data = result)
summary(fit.lm2)

VIF(fit.lm2)

fit.lm2_reduced <- lm(Real.World.MPG ~ production, data = result)
summary(fit.lm2_reduced)

anova(fit.lm2_reduced, fit.lm2, test = "F")

```

First, we have the full model which contains all the predictors from the dataset, including country, year, car weight, footprint, horsepower, fuel delivery, and engine displacement. Since only the variable *Country* is categorical and others are all quantitative, we decide to employ a Multiple Linear Regression Model here.

| Variables           | Coefficients  | P-values | Is it significant|
| ------------------- |:-------------:| --------:|:----------------:|
| (Intercept)         |176.212571     | 8.84e-09 | Yes              |
| CountryGerman       |-19.563854     | 1.17e-09 | Yes              |
| CountryJapan        |-9.024095      | 0.004156 | Yes              |
| CountryKorea        |-9.809526      | 0.006774 | Yes              |
| year2015            |0.361388       | 0.259330 | No               |
| production          |0.150317       | 0.298521 | No               |
| Weight              |-0.001618      | 0.746582 | No               |
| Footprint           |-2.866676      | 0.000321 | Yes              |
| Horsepower          |0.204628       | 3.23e-08 | Yes              |
| Fuel.Delivery.GDI   |-3.075369      | 0.130999 | No               |
| Engine.Displacement |-0.259394      | < 2e-16  | Yes              |

According to the summary table above, variables *Country*, *Horsepower* ，*Footprint* and *Engine Displacement* are all significant. For *Country*, it indicates that cars' emission in Korea, Japan, German are all significant compare to cars' emission in America. Additionally, the concentration of carbon dioxide in America is at least 6 times as high as the concentration of carbon dioxide in the other countries. For *Horsepower*, holding other predictors constant, the concentration of CO2 will increase by 0.25 grams per mile for each additional horsepower. For Footprint, holding other predictors constant, the concentration of CO2 will decrease by 15.54 grams per mile for each additional rate of fuel delivery.


The formula of the model would be:

*Real.World.MPG* = 176.212571 - 19.56385*CountryGerman* - 9.024095*CountryJapan* - 9.809526*CountryKorea* - 2.866676*Footprint* + 0.204628*Horsepower* - 0.259394*Engine.Displacement*

Here, we have a R-squared value equals to 0.9544 which means that nearly 95.44% of the response data can be explained by this model.


| Variables           | GVIF          | Df  | GVIF^(1/(2*Df))  |
| ------------------- |:-------------:| ---:|:----------------:|
| Country             |39.685734      | 3   | 1.846882         |
| year2015            |1.188785       | 1   | 1.090314         |
| production          |7.300865       | 1   | 2.702011         |
| Weight              |18.052875      | 1   | 4.248867         |
| Footprint           |19.710171      | 1   | 4.439614         |
| Horsepower          |17.474682      | 1   | 4.180273         |
| Fuel.Delivery.GDI   |2.389717       | 1   | 1.545871         |
| Engine.Displacement |5.53459        | 1   | 2.352571         |

Based on the EDA, we noticed that there might have correlation between some variables. Thus, here we use VIF function to detect multicollinearity. From the result, the most apparent difference is that the value of VIFs are all down to satisfactory values; they are all less than 5. By removing the structural multicollinearity, we can see that there is some multicollinearity in our data, but it is not severe enough to warrant further corrective measures.

Since our research question is to determine the relationship between the concentration of CO2 and car sales, the variables *production* is not significant in our full model, which indicates that there is no significant relationship between the concentration of CO2 and car sales. Thus, we employ a single linear model for further analysis. This would be a reduced model which only includes one predictor *production*.


| Variables           | Coefficients  | P-values | Is it significant|
| ------------------- |:-------------:| --------:|:----------------:|
| (Intercept)         | 41.2520       | < 2e-16  | Yes              |
| Production          |-0.8247        | 0.000666 | Yes              |

According to the summary table, we found that the variable *production* is significant with a very small p-value 0.000666. Therefore, the car sales have significantly positive impact on the concentration of CO2 in this reduced model. However, the R-squared for this model is only 0.1219 which is not good enough.

In order to determine the final model for our data, we decide to use ANOVA function to apply F test for these two models: full and reduced. This F test is a generalization of the t-test for individual model coefficients which can be used to perform significance tests on nested models. Here we have our null hypothesis which is just the reduced model and the alternative hypothesis is the full model.


| Model   | F- statistics | P-values | Is it significant|
| ------- |:-------------:| --------:|:----------------:|
| 1       |               |          |                  |
| 2       |167.22         | <2.2e-16 | Yes              |

From the result, we could see that we have statistically signicant evidence (F = 167.22 and p-value < 2.2e-16) to reject our null hypothesis. With that being said, the full model is more appropriate for our data. Thus, we determine the full model as our final model by F-test.

The final model would be:*Real.World.MPG* = 176.212571 - 19.56385*CountryGerman* - 9.024095*CountryJapan* - 9.809526*CountryKorea* - 2.866676*Footprint* + 0.204628*Horsepower* - 0.259394*Engine.Displacement*

To answer our research question 2 based on this model, we conclude that there is no significant relationship between the concentration of CO2 and car sales.


# Recommendations 

For the first research question, we found that the *Fuel Delivery GDI* and *weight* variables are significant. Thus, we determine that these two variables are the two main factors of car industry impact on the environment (represent by CO2 output). The *Real World CO2* represents the environment, when the CO2 goes up which means the environment is worse and when the CO2 goes down which means the environment are getting better. And the weight represent the cars' weight.  According to this result, we can see that the there is no relationship between COVID-19 and the environment, however, the *Fuel Delivery GDI* rate and *Weight* of cars are related to the environment.

For the second research question, we conclude that there is no significant relationship between the concentration of CO2 and car sales. Therefore, car sales will not contribute to our environment pollution by producing more carbon dioxide. Compared to the car sales, other predictors including different countries, car weights, horsepower, and fuel delivery seems more likely to contribute to the environment pollution by causing more carbon dioxide emission.

There is also some concerns in our models. The response variable: concentration of carbon dioxide is measured based on each year while the car sales is measured based on each month. Due to the COVID-19, the sudden drop of car sales only occur in March, April, May, and June in 2020. Only few months of changing might not have significant impacts on the environment compared to other factors. Thus, this might be one of the reasons that car sales is not significant in our final model.

# Resources 
### Source 1

US Environmental Protection Agency. 2021 EPA Automotive Trends Report. Data available at www.epa.gov/automotive-trends/explore-automotive-trends-data. Accessed November 03, 2021

The first source we used is provided by the U.S. Environment Protection Agency (EPA). EPA has collected data on every new light-duty vehicle model sold in the United States since 1975, either from testing performed by EPA at the National Vehicle Fuel and Emissions Laboratory in Ann Arbor, Michigan, or directly from manufacturers using official EPA test procedures. These data are collected to support several important national programs, including EPA criteria pollutants and GHG standards, the U.S. Department of Transportation’s National Highway Traffic Safety Administration (NHTSA) Corporate Average Fuel Economy (CAFE) standards, and vehicle Fuel Economy and Environment labels. Thus, this expansive data set allows EPA to provide a uniquely comprehensive analysis of the automobile industry over the last 45 years.

### Source 2

MarkLines Source Center. (2021, January 6). USA - Flash report, Sales volume, 2020. Retrieved December 6, 2021, from https://www.marklines.com/en/statistics/flash_sales/automotive-sales-in-usa-by-month-2020.

The second data source is from the Automotive Industry Portal, MarkLines. This data source contains each monthly sale in 2020. In addition, we also used extract the information for 2015 and 2019 from this website. MarkLine is intend to develop and grow the automotive industry by providing information services. This specific dataset was collected every month in 2020 and stop on January 6th, 2021. All of this information is collected through purchases from third-party sources, as well as partnerships with other companies. We found this dataset on their company's official website. 

### Source 3

Professor name: Sherry Wu

Contact information:

510 Kern Building

University Park, PA 16802

Email: sqw5740@psu.edu

Phone: (814) 865-4921

Introduction:

Sherry Wu is a visiting assistant professor at Penn State University in the department of Economics. She is particularly interested in industrial organization. Dr.Wu is also the professor in the environmental economics class. Since our research goal is to analyze the impact of the automotive industry on economy and environment, we think Dr.Wu will be very helpful in giving advice for our project.


# Additional Considerations


# Technical Appendix  

```{r assumptions}
par(mfrow = c(2, 2))
plot(fit.lm1)
```

We drew Residual vs. Fitted plots and Normal Q_Q plots to check assumptions. First of all, the residual vs. fitted plots show that the Linearity is met for all six models since those dots are randomly spaced around the line of residual(red line) that is 0. Secondly, the Independent assumption is met since every child is an individual observation unit. Then, from the Normal Q_Q plots, we observed that most of the dots are along the dashed line. We can state that the normality is met. Last but not least, according to residual vs. fitted plots, equal variance is also met. Distances between each dot seem to be the same.


### R Script
```{r ref.label=c('Front Matter', 'variable', 'Data Cleaning', 'barplot', 'correlation','model1','model2','assumptions'), echo=TRUE, eval=FALSE}
# Reprinted code chunks used previously for analysis
```



